---
title: "Counts Without Complexes Analysis for *Hyla chrysoscelis*"
author: "Lauren White"
date: "April 12, 2018"
output: html_document
---

##Load libraries, dataset, and edgelist
```{r}
library(igraph)
#edgelist2<-read.csv("frogedgelist.csv")
edgelist<-read.csv("frogedgelist_cwoc.csv")
#cwc<-read.csv("CountsWithComplexes.csv")
cwoc<-read.csv("CountsWithoutComplexes.csv")

```

##Translate into a weighted affiliation matrix
Using sparse matrices
```{r}
library('Matrix')
A <- spMatrix(nrow=length(unique(edgelist$Species)),
        ncol=length(unique(edgelist$Location)),
        i = as.numeric(factor(edgelist$Species)),
        j = as.numeric(factor(edgelist$Location)),
        x = rep(1, length(as.numeric(edgelist$Species))) )
row.names(A) <- levels(factor(edgelist$Species))
colnames(A) <- levels(factor(edgelist$Location))
A

#Frogs have edges if they were at same transect & stop on same day
Arow <- tcrossprod(A)
Arow

```

##Global network for species that co-call with *Hyla chrysoscelis*
A global network with all the frogs that co-call with *Hyla chrysoscelis*. Unweighted edges.
```{r}

#which row in the association matrix corresponds to Hyla chrysoscelis
species<-which(rownames(Arow)=="Hyla chrysoscelis")
cocall<-Arow[,species] #Row in matrix containing Hylea chrysoscelis 

#Which species co-call with Hyla cinera (edge weight > 0)
cocall<-which(cocall>0) 

#Generate sub containing only species that co-call with Hyla chrysoscelis
mat_all<-Arow[which(rownames(Arow)%in% names(cocall)), which(colnames(Arow) %in% names(cocall))] 

mat_all[mat_all > 1] <- 1


#Create igraph object
g<-graph_from_adjacency_matrix(mat_all, mode = "undirected", weighted = NULL, diag = FALSE,  add.colnames = NULL, add.rownames = NA)
summary(g)

V(g)$number=as.character(cwoc$Species.ID[match(V(g)$name,cwoc$Species)]) # This code says to create a vertex attribute called "Sex" by extracting the value of the column "Sex" in the attributes file when the Bird ID number matches the vertex name.

#Optional: assign the "IsHyla" attribute as the vertex color (Just comment out if you want everything the same color)
attrib_all<-data.frame(Species=names(cocall), IsHyla=names(cocall)=="Hyla chrysoscelis")
V(g)$IsHyla=as.character(attrib_all$IsHyla[match(V(g)$name, attrib_all$Species)])
V(g)$color=V(g)$IsHyla
V(g)$color=gsub(FALSE,"white",V(g)$color)
V(g)$color=gsub(TRUE,"white",V(g)$color)


#Look at degree distribution for glboal network
hist(degree(g))
library(ggplot2)

tiff("Chrysoscelis_Global_dd_cwoc.tiff", height =10 , width =12, units = "cm", compression = "lzw", res = 1200)
qplot(degree(g), geom="histogram", main = "Degree distribution: Co-calling with Hyla chrysoscelis", xlab = "degree", fill=I("blue"), col=I("black"), alpha=I(.2),   xlim=c(0,60))
dev.off()

#Reduce labeling relative
V(g)$label.cex = .60
l<-layout.fruchterman.reingold(g)

#Note: #21 corresponds to the Species.ID for *Hyla chrysoscelis*
tiff("Chrysoscelis_Global_network_cwoc_labeled.tiff", height =10 , width =10, units = "cm", compression = "lzw", res = 1200)
plot.igraph(g,vertex.label=V(g)$number, layout=l)
dev.off()

tiff("Chrysoscelis_Global_network_cwoc_unlabeled.tiff", height =10 , width =10, units = "cm", compression = "lzw", res = 1200)
plot.igraph(g,vertex.label=NA, layout=l)
dev.off()

#Note: you can adjust node location manually using this command:
tkplot(g)

```

##Top ten co-callers 
A network with *Hyla chrysoscelis* and the 10 frogs that most commonly co-call. With weighted edges. 

```{r}
species<-which(rownames(Arow)=="Hyla chrysoscelis")
cocall<-Arow[,species] #Row in matrix containing Hylea chrysoscelis 
cocall<-sort(cocall, decreasing = TRUE)

topten<-cocall[1:11] #includeing Hyla chrysoscelis (adjust last number in sequence to get top x number of co-calling species)

mat10<-Arow[which(rownames(Arow)%in% names(topten)), which(colnames(Arow) %in% names(topten))] #subnetwork containing only top ten species that co-call with Hyla chrysoscelis

h<-graph_from_adjacency_matrix(mat10, mode = "undirected", weighted = TRUE, diag = FALSE, add.colnames = NULL, add.rownames = NA)
summary(h)
E(h)$weight #weighted edges this time

attrib<-data.frame(Species=names(topten), Weight=topten, IsHyla=names(topten)=="Hyla chrysoscelis") #create an attribute data frame- is the species the focal species, or not?

#assign as vertex attribute- is species focal species or not?
V(h)$IsHyla=as.character(attrib$IsHyla[match(V(h)$name,attrib$Species)])
V(h)$color=V(h)$IsHyla #assign the "IsHyla" attribute as the vertex color
V(h)$color=gsub(FALSE,"white",V(h)$color)
V(h)$color=gsub(TRUE,"white",V(h)$color)


l <- layout_with_fr(h)
l2 <- layout_as_star(h, center = V(h)[4], order = NULL)
l3 <-layout.circle(h)

#reduce vertex label size
V(h)$label.cex = .30

tiff("Chrysoscelis_Topten_star_cwoc_labeled.tiff", height =10 , width =10, units = "cm", compression = "lzw", res = 1200)
plot.igraph(h,vertex.label=V(h)$name,layout=l2,edge.width=E(h)$weight/750)
dev.off()

tiff("Chrysoscelis_Topten_star_cwoc_ unlabeled.tiff", height =10 , width =10, units = "cm", compression = "lzw", res = 1200)
plot.igraph(h,vertex.label=NA,layout=l2,edge.width=E(h)$weight/750)
dev.off()

tiff("Chrysoscelis_Topten_circle_cwoc_labeled.tiff", height =10 , width =10, units = "cm", compression = "lzw", res = 1200)
plot.igraph(h,vertex.label=V(h)$name,layout=l3,edge.width=E(h)$weight/750)
dev.off()

tiff("Chrysoscelis_Topten_circle_cwoc_unlabeled.tiff", height =10 , width =10, units = "cm", compression = "lzw", res = 1200)
plot.igraph(h,vertex.label=NA,layout=l3,edge.width=E(h)$weight/750)
dev.off()

```